Bandit Multiclass Classification

### 2018-08-10 main.tex
.

%\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
% For citations
\usepackage{natbib}
\usepackage{amsthm}
% For algorithms
%\usepackage[algcompatible]{algpseudocode}
%\usepackage{algorithm}
%\usepackage{algorithmicx}
%\usepackage[noend]{algcompatible}
\usepackage[vlined,linesnumbered,ruled]{algorithm2e}
\usepackage{bbm}
\usepackage{amsfonts}
\usepackage{amsmath}           
\usepackage{mathtools}    
\usepackage{amsopn}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage{soul}
%%%%%%%%%%%%%%%%%% toc 
\usepackage{scrwfile}
\TOCclone[\contentsname~(\appendixname)]{toc}{atoc}
\newcommand\StartAppendixEntries{}
\AfterTOCHead[toc]{%
  \renewcommand\StartAppendixEntries{\value{tocdepth}=-10000\relax}%
}
\AfterTOCHead[atoc]{%
  \edef\maintocdepth{\the\value{tocdepth}}%
  \value{tocdepth}=-10000\relax%
  \renewcommand\StartAppendixEntries{\value{tocdepth}=\maintocdepth\relax}%
}
\newcommand*\appendixwithtoc{%
  \cleardoublepage
  \appendix
  \addtocontents{toc}{\protect\StartAppendixEntries}
  \listofatoc
}
\usepackage{blindtext}
\usepackage{color}
%%%%%%%%%%%%%%%%%% toc

@@

\section{One-versus-all Kernel Perceptron}
\subsection{One-versus-all Perceptron}
Our assumption of linearly separable with a margin is 
\begin{align}
 (W^*x_t)_{y_t} \geq (W^*x_t)_{y} + \gamma, \ \forall y\neq y_t. \label{eqn:weaker}
\end{align}
As discussed in Section~\ref{section: difficulty}, it seems hard to make update when $\tilde{y}_t\neq y_t$ and achieve a constant and polynomial error bound.

@@

\subsection{One-versus-all Kernel Perceptron}
With the polynomial kernel defined in \cite{klivans2004learning}, we can transform the weaker assumption \eqref{eqn:weaker} in the original feature space to the stronger one \eqref{eqn:stronger} in a transformed feature space. Indeed, in the original feature space, class $i$ corresponds to an intersection of $K-1$ halfspaces: $ \{x: (w_i^*-w_j^*)^\top x \geq 0, \forall j\neq i\} $, which is the subject of \cite{klivans2004learning} (here, $w_i^{*\top}$ equals to $\e_i^\top W^*$ defined above). Directly using their kernel construction, we can have margin $ \left(\frac{\gamma}{d}\right)^{\Omega(K\log K\log (1/\gamma))} $ in the transformed feature space. Running kernelized version of Algorithm~\ref{alg:ova}, we can get $ K^2\left(\frac{d}{\gamma}\right)^{\mathcal{O}(K\log K\log (1/\gamma))} $ error bound directly.

>>>>

%\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
% For citations
\usepackage{natbib}
\usepackage{amsthm}
\usepackage{makecell}
% For algorithms
%\usepackage[algcompatible]{algpseudocode}
%\usepackage{algorithm}
%\usepackage{algorithmicx}
%\usepackage[noend]{algcompatible}
\usepackage[vlined,linesnumbered,ruled]{algorithm2e}
\usepackage{bbm}
\usepackage{amsfonts}
\usepackage{amsmath}           
\usepackage{mathtools}    
\usepackage{amsopn}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage{soul}
%%%%%%%%%%%%%%%%%% toc 
\usepackage{scrwfile}
\TOCclone[\contentsname~(\appendixname)]{toc}{atoc}
\newcommand\StartAppendixEntries{}
\AfterTOCHead[toc]{%
  \renewcommand\StartAppendixEntries{\value{tocdepth}=-10000\relax}%
}
\AfterTOCHead[atoc]{%
  \edef\maintocdepth{\the\value{tocdepth}}%
  \value{tocdepth}=-10000\relax%
  \renewcommand\StartAppendixEntries{\value{tocdepth}=\maintocdepth\relax}%
}
\newcommand*\appendixwithtoc{%
  \cleardoublepage
  \appendix
  \addtocontents{toc}{\protect\StartAppendixEntries}
  \listofatoc
}
\usepackage{blindtext}
\usepackage{color}
%%%%%%%%%%%%%%%%%% toc

@@

\section{One-versus-all Perceptron}
Our assumption of linearly separable with a margin is 
\begin{align}
 (W^*x_t)_{y_t} \geq (W^*x_t)_{y} + \gamma, \ \forall y\neq y_t. \label{eqn:weaker}
\end{align}
As discussed in Section~\ref{section: difficulty}, it seems hard to make update when $\tilde{y}_t\neq y_t$ and achieve a constant and polynomial error bound.

@@

\section{One-versus-all Kernel Perceptron}
With the polynomial kernel defined in \cite{klivans2004learning}, we can transform the weaker assumption \eqref{eqn:weaker} in the original feature space to the stronger one \eqref{eqn:stronger} in a transformed feature space. Indeed, in the original feature space, class $i$ corresponds to an intersection of $K-1$ halfspaces: $ \{x: (w_i^*-w_j^*)^\top x \geq 0, \forall j\neq i\} $, which is the subject of \cite{klivans2004learning} (here, $w_i^{*\top}$ equals to $\e_i^\top W^*$ defined above). Directly using their kernel construction, we can have margin $ \left(\frac{\gamma}{d}\right)^{\Omega(K\log K\log (1/\gamma))} $ in the transformed feature space. Running kernelized version of Algorithm~\ref{alg:ova}, we can get $ K^2\left(\frac{d}{\gamma}\right)^{\mathcal{O}(K\log K\log (1/\gamma))} $ error bound directly.

\subsection{Refinement for \cite{klivans2004learning}'s Fact 1}
\begin{lemma}
   For $i=1,\ldots, \ell$ let $q^{(i)}(x)=\sum_S c^{(i)}_{S} x_S $ be a polynomial over $x_1, \ldots, x_d$ with $\|q^{(i)}\|^2\leq M_i$. Then (1) if $q^{(1)}\ldots q^{(\ell)}$ has degree at most $\deg$, we have $\|q^{(1)}\ldots q^{(\ell)}\|^2 \leq (\deg)^{O(\deg)} \prod_i M_i$, and (2) we have $\|q^{(1)}+\ldots+q^{(\ell)}\|^2\leq \ell(M_1+\ldots+M_\ell)$. 
\end{lemma}
\begin{proof}
For the first bound, we bound the ratio between the following two values:  $ \|q^{(1)}\ldots q^{(\ell)}\|^2 $ and $\|q^{(1)}\|^2\ldots \|q^{(\ell)}\|^2$. 
\begin{align}
    n_1&=\prod_{i=1}^\ell \|q^{(i)}\|^2 
    = \prod_{i=1}^\ell \left(\sum_{S_i} \left(c^{(i)}_{S_i}\right)^2 \right)
    = \sum_{(S_1,\ldots,S_\ell)}  \left(\prod_{i=1}^\ell \left(c^{(i)}_{S_i}\right)^2 \right)
    = \sum_{(S_1,\ldots,S_\ell)}  \left(\prod_{i=1}^\ell c^{(i)}_{S_i}\right)^2 \nonumber\\
    &= \sum_S \sum_{\substack{(S_1,\ldots,S_\ell): \\ S_1\times\ldots S_\ell=S}}  \left(\prod_{i=1}^\ell c^{(i)}_{S_i}\right)^2
\end{align}
\begin{align}
    n_2=\|q^{(1)}\ldots q^{(\ell)}\|^2 = \sum_{S} c_S^2 
    = \sum_S \left( \sum_{\substack{(S_1,\ldots, S_\ell): \\ S_1\times\ldots\times S_\ell=S }} \left(c_{S_1}^{(1)}\ldots c_{S_\ell}^{(\ell)} \right) \right)^2 
    = \sum_S \left( \sum_{\substack{(S_1,\ldots, S_\ell): \\ S_1\times\ldots\times S_\ell=S }} \prod_{i=1}^\ell c_{S_i}^{(i)} \right)^2 
\end{align}
Let $M$ be an upper bound of the number of terms involved in the summation $ \sum_{\substack{(S_1,\ldots, S_\ell): \\ S_1\times\ldots\times S_\ell=S }} $, then by Cauchy-Schwarz's inequality we have $ n_2\leq Mn_1 $.

$M$ counts the number of different $(S_1,\ldots, S_\ell)$'s with $S_1\times \ldots \times S_\ell=S$. Since $S$ has degree at most $\deg$, we can bound $M$ by $ \ell^{\deg}$.

The second bound can be obtained by applying Cauchy-Schwarz once.

\end{proof}

\subsection{Refinement for \cite{klivans2004learning}'s Theorem 10}
\begin{lemma}
Under the same condition as in \cite{klivans2004learning}'s Theorem 10, the PTF has margin on $X$ is at least $(1/t)^{O(r\log r + r\log\log t)}$. 
\end{lemma}
\begin{proof}
We simply follow the construction in the original paper. $\|1-w^i\cdot x\|^2\leq 4$ can imply $\|(1-w^i\cdot x)^j\|^2\leq j^{O(j)}4^j \leq j^{O(j)}$. Then $\|a_j(1-w^i\cdot x)^j\|^2\leq 2^{2r}r^{O(r)}=r^{O(r)}$ follows. Thus $\|T_r(1-w^i\cdot x)\|^2=\|\sum_{j=0}^r a_j (1-w^i\cdot x)^j\|^2 \leq (r+1)^2 r^{O(r)} = r^{O(r)}$. Then, $\left(P(w^i\cdot x)\right)^{\log 2t}\leq (\log t)^{O(r\log t)}\times r^{O(r\log t)}\leq (r\log t)^{O(r\log t)}$. Finally, $\|p\|^2\leq (t+1)^2 (r\log t)^{O(r\log t)} \leq (t+1)^2 \left(  t^{O(r\log r + r\log\log t)}\right) = t^{O(r\log r + r\log\log t)}$.  
\end{proof}

\subsection{Refinement for \cite{klivans2004learning}'s Theorem 7}
\begin{lemma}
Under the same condition as in \cite{klivans2004learning}'s Theorem 7, the PTF has margin on $X$ is at least $\left( \frac{\rho}{t\log t \log \frac{1}{\rho}} \right)^{O(t\log t\log 1/\rho)}$. 
\end{lemma}
\begin{proof}
Using the same construction, we bound $\|p\|$. First, we have $\|\frac{2w^i\cdot x}{\rho}\|^2\leq \frac{4}{\rho^2}$ and $\|\left(\frac{2w^i\cdot x}{\rho}\right)^j\|^2\leq j^j\left(\frac{4}{\rho^2}\right)^j=\left(\frac{4j}{\rho^2}\right)^j$. $a(x), b(x)$ are polynomials of degree $O(\log t\log \frac{1}{\rho})$ with coefficients of magnitude $\left(\frac{1}{\rho}\right)^{O(\log t\log 1/\rho)}$. Thus 
\begin{align*}
    \|a(2w^i\cdot x/\rho)\|^2 &\leq 
    \left( \frac{\log t \log \frac{1}{\rho}}{\rho} \right)^{O(\log t\log 1/\rho)}  \times  \left(\frac{1}{\rho}\right)^{O(\log t\log 1/\rho)}\\
    &\leq \left( \frac{\log t \log \frac{1}{\rho}}{\rho} \right)^{O(\log t\log 1/\rho)}.
\end{align*}
Same holds for $\|b(2w^i\cdot x/\rho)\|^2$. Finally we have $\|B(x)\|^2 \leq (t)^{O(t\log t\log 1/\rho)} \times \left( \frac{\log t \log \frac{1}{\rho}}{\rho} \right)^{O(t\log t\log 1/\rho)} = \left( \frac{t\log t \log \frac{1}{\rho}}{\rho} \right)^{O(t\log t\log 1/\rho)}$
\end{proof}

\section{Regret Lower Bound for Explore-then-Exploit Algorithms {\color{red}[TODO]}}
